A holographic approach to the six-dimensional superconformal index

### 2022-10-14 fivebranes/finite.tex
merge

\section{Conjectures for operators on fivebranes}
\label{s:finite}

@@

Recall that our conjecture for the factorization algebra associated to the holomorphic twist of the six-dimensional worldvolume theory associated to a stack of two fivebranes is $\Obs_2 \simeq \clie_\bu(\cG_{2,c}) \cong \clie_\bu(\cG_{1,c}) \otimes \clie_\bu(\til \cG_{2,c})$. 
And after removing the center of mass degrees of freedom, our conjecture is $\til \Obs_2 \simeq \clie_\bu(\til \cG_{2,c})$.

>>>>

\section{Conjectures for indices of operators on fivebranes}
\label{s:finite}

@@

Recall that our conjecture for the space of local operators associated to the holomorphic twist of the six-dimensional worldvolume theory on a stack of two fivebranes is $\Obs_2 (0) \simeq \clie_\bu(\cG_{2,c})(0) \cong \clie_\bu(\cG_{1,c})(0) \otimes \clie_\bu(\til \cG_{2,c})(0)$. 
And after removing the center of mass degrees of freedom, our conjecture is $\til \Obs_2 \simeq \clie_\bu(\til \cG_{2,c})$.

### 2022-10-14 fivebranes/index.tex
merge

In \cite{RSW} we have shown that solutions to equations of motion of our eleven-dimensional theory in the twisted $AdS_{7}\times S^{4}$ background recalled in the previous subsection contains the symmetry algebra $\lie{osp}(6|2)$. This is precisely the twist of the superconformal algebra we just discussed, so this statement may be interpreted as the twisted avatar of the fact that $\lie{osp}(8|4)$ acts as isometries on $AdS_{7}\times S^{4}.$ An easy consequence of the result of \cite{RSW} and the definition of $\cH_{sugra}$ in~\ref{hilbert} is that the twisted symmetry algebra $\lie{osp}(6|2)$ acts on $\cH_{sugra}$.

>>>>

In \cite{RSW} we have shown that solutions to equations of motion of our eleven-dimensional theory in the twisted $AdS_{7}\times S^{4}$ background recalled in the previous subsection contains the symmetry algebra $\lie{osp}(6|2)$. This is precisely the twist of the superconformal algebra we just discussed, so this statement may be interpreted as the twisted avatar of the fact that $\lie{osp}(8|4)$ acts as isometries on $AdS_{7}\times S^{4}.$ An easy consequence of the result of \cite{RSW} and the definition of $\cH_{sugra}$ in~\ref{dfn:states} is that the twisted symmetry algebra $\lie{osp}(6|2)$ acts on $\cH_{sugra}$.
